refractory erectile dysfunction (by ArticleAggregator_v05)

### 2023-02-22 ArticleAggregatorCS.qmd
PubMed search skipped

>>>>

## Merge EB and GS ony
```{r}
#| label: Merge results from embase (eb), Google Scholar (gs), and PubMed (pm)
eb <- read_xlsx(glue("{aa_path}eb_to_merge.xlsx"))
gs <- read_xlsx(glue("{aa_path}gs_to_merge.xlsx"))
# pm <- read_xlsx(glue("{aa_path}pm_to_merge.xlsx"))

eg <- bind_rows(eb, gs) %>%
  mutate(Status=NA) %>% 
  mutate(Priority=NA) %>% 
  arrange(desc(Year), Author, Src) %>% 
  select(Status, Priority, everything())
# rm(list=ls()[!ls() %in% c("eg")])
write_xlsx(eg, glue("{aa_path}eg_v02.xlsx"))
```
